pdp: An R Package for Constructing Partial Dependence Plots

### 2016-12-15 manuscript/greenwell.tex
tweaks based on review comments

\citet{harrison-1978-hedonic} were among the first to analyze the well-known Boston housing data. One of their goals was to find a housing value equation using data on median housing values from 506 census tracts in the suburbs of Boston from the 1970 census. The prediction equation from one of there regression analyses is reproduced in Equation~\eqref{eqn:boston}. \citet{harrison-1978-hedonic} took great care and time to find this model which obtained an $R^2$ of roughly 0.81. Part of the payoff for there efforts was a reaonable fitting model with an interpretable equation. For example, the equation tells us that an increase in median home value is associated with an increase in the average number of rooms per dwelling.
\begin{equation}
\label{eqn:boston}
\begin{split}
\widehat{\log\left(MV\right)} &= 9.76 + 0.0063 RM^2 + 8.98\times10^{-5} AGE - 0.19\log\left(DIS\right) + 0.096\log\left(RAD\right) \\
  &\quad - 4.20\times10^{-4} TAX - 0.031 PTRATIO + 0.36\left(B - 0.63\right)^2 - 0.37\log\left(LSTAT\right) \\
  &\quad - 0.012 CRIM + 8.03\time10^{-5} ZN + 2.41\times10^{-4} INDUS + 0.088 CHAS - 0.0064 NOX^2
\end{split}
\end{equation}

Many modern nonparametric models, however, can fit the data automatically in seconds---typically with higher accuracy. The downfall, however, is some loss of interpretation; for example, there is usually no prediction formula like in Equation~\eqref{eqn:boston}. Fortunately, methods like boosting and random forest have a natural way to assign variable importance scroes to the predictors which helps gives some insight into the data.

>>>>

\citet{harrison-1978-hedonic} were among the first to analyze the well-known Boston housing data. One of their goals was to find a housing value equation using data on median housing values from 506 census tracts in the suburbs of Boston from the 1970 census. The prediction equation from one of there regression analyses is reproduced in Equation~\eqref{eqn:boston}. \citet{harrison-1978-hedonic} took great care and time to find this model which obtained an $R^2$ of roughly 0.81. Part of the payoff for there efforts was a reasonable fitting model with an interpretable equation. For example, the equation tells us that an increase in median home value is associated with an increase in the average number of rooms per dwelling.
\begin{equation}
\label{eqn:boston}
\begin{split}
\widehat{\log\left(MV\right)} &= 9.76 + 0.0063 RM^2 + 8.98\times10^{-5} AGE - 0.19\log\left(DIS\right) + 0.096\log\left(RAD\right) \\
  &\quad - 4.20\times10^{-4} TAX - 0.031 PTRATIO + 0.36\left(B - 0.63\right)^2 - 0.37\log\left(LSTAT\right) \\
  &\quad - 0.012 CRIM + 8.03\time10^{-5} ZN + 2.41\times10^{-4} INDUS + 0.088 CHAS - 0.0064 NOX^2
\end{split}
\end{equation}

Many modern nonparametric models, however, can fit the data automatically in seconds---typically with higher accuracy. The downfall, however, is some loss of interpretation; for example, there is usually no prediction formula like in Equation~\eqref{eqn:boston}. Fortunately, these methods can still provide insight into the data, but it is not in the form of simple equations. For example, many modern methods, like boosting and random forests, can assign importance scores to all of the predictors.
